### 2018-08-07 paper/evaluation.tex

@@

>>>>

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=0.8\columnwidth]{figures/completion_vs_size.pdf}

  \caption{\label{fig:completion_vs_size}
  Success rate of the file transfer ordered by size of file.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files.pdf}

  \caption{\label{fig:bw_and_pending_files}Traffic during one experiment.
  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
\end{figure}

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files_log.pdf}

  \caption{\label{fig:bw_and_pending_files_log}Traffic during one experiment.
  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
\end{figure}
